---
title: "CCISS Report"
concept author: Will MacKenzie
script author: Kiri Daust + Will MacKenzie
output: html_document
---

# Copyright 2021 Province of British Columbia
# 
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
# 
# http://www.apache.org/licenses/LICENSE-2.0
# 
# Unless required by applicable law or agreed to in writing, software
# distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and
# limitations under the License.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
require(data.table)
require(foreach)
require(tidyverse)
require(DBI)
require(sf)
library(here)
require(RPostgreSQL)
library(raster)
library(matrixStats)
library(Rcpp)
require(tictoc)
require(ggplot2)
require(ggthemes)
require(tmap)
#install.packages("tmap")
```

This script is a major reworking of the initial CCISS script. Instead of loading the random forest model and predicting on the spot, the script connects to a database to pull already predicted data. The edatopic overlap function has been totally rewritten in data.table, and is much faster.

#### Source functions

```{r source}
Rcpp::sourceCpp("0CCISS_Cfn.cpp")
source("1CCISS_Data.R")
source("2CCISS_EdaOverlap.R")
source("3CCISS_Suit.R")

cloud_dir <- ("./data_tables/")
# if(dir.exists("E:/Sync/CCISS_data/")){
#   cloud_dir <- "E:/Sync/CCISS_data/"
# }else{
#   cloud_dir <- "C:/Users/kirid/Desktop/Work2021/"
# }
E1 <- fread(paste0(cloud_dir, "Edatopic_v11_22.csv")) 
S1 <- fread(paste0(cloud_dir,"Feasibility_v11_22.csv"))

R1 <- fread(paste0(cloud_dir,"RuleTable.csv"))
F1 <- fread(paste0(cloud_dir,"FeasibilityLabels.csv"))

```

Pull predicted data from PostGres database sitting on server in Will's kitchen.
Extract data given hex id values. Output is predicted BGCs, with the proportion of models that predict them.


```{r get BGC.pred at sites}
##load csv with lat and long columns
loc_name <- "WilliamsLake" ## name of trial run
pointDat <- fread("./test_locations/WilliamsLake_Locations.csv")
test_siteno <- dbGetHexID(pointDat,host = "smithersresearch.ca") ## returns hex number from location for testing
tic()
# test_siteno <- dbGetHexID(pointDat, host = "FLNRServer")
toc()
ID1_testsite <- cbind(pointDat, test_siteno) %>% dplyr::rename(SiteNo = test_siteno)
# test_siteno <- c(3084611 ,3088043 ,3088100 ,3093240 ,3096701 ,3103527 ,3103529 ,3103530 ,3105299 ,3115525) #hex numbers
average <- FALSE
BGC <- dbGetCCISS(test_siteno, avg = average, host = "smithersresearch.ca") 
#BGC <- BGC %>% filter (BGC == "IDFxh2")


```

#### Edatopic Overlap

This function is a much faster (~3000x) reworking of the original nested foreach loops. Input is bgc predictions (from above) and output is future site series.

```{r edaOverlap}
#E1 <- E1 %>% filter(BGC == "PPxh1") ##edatopic grids
SSPreds <- edatopicOverlap(BGC,Edatope = E1)
```

#### Calculate Feasibility and Statistics

```{r merge suit}

cciss_res <- ccissOutput(SSPred = SSPreds, suit = S1, rules = R1, feasFlag = F1)
CCISS_Summary <- as.data.frame (cciss_res$Summary)
CCISS_Summary <- left_join(CCISS_Summary,ID1_testsite) %>% dplyr::select(ID1, everything())#%>% filter(!ID1 == "test")
CCISS_Sites <- CCISS_Summary %>% dplyr::select(ID1, Lat, Long)

CCISS_Raw <- as.data.frame (cciss_res$Raw)
CCISS_Raw  <- left_join(CCISS_Raw ,ID1_testsite) %>% dplyr::select(-ID2, -ModAgree, - SuitDiff, -Lat, -Long, -Elev) %>% 
  dplyr::select(ID1, everything()) %>% 
  filter(!ID1 == "test") %>% mutate(across(NewSuit, round, 0)) %>% mutate(across(c(`1`, `2`, `3`, X), round, 2))

```

1. BGC ratios stack bar from BGC table
2. Feasibility report from CCISS_Summary + CCISS_Raw tables
3. Map of locations from CCISS_Sites