---
title: "Comparison of predicted BGC ratios by GCM"
author: "Will MacKenzie"
date: "14/10/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

## spatial climates
library(data.table)
library(sf)
library(RPostgreSQL)
library(dplyr)
library(foreach)
library(rmapshaper)
library(tictoc)
library(rasterVis)
library(raster)
library(ccissr)
require(tidyverse)
require(labdsv)
require (factoextra)
```

Based on predictions from a provincial 2km grid of points. 
First analysis based on all GCMS and then a second round with 3 poor performing GCMs removed.
The intent is to find GCM families and representative units based on BGC outcomes of climate futures.
```{r download data, include=FALSE}
##connect to cciss database
# drv <- dbDriver("PostgreSQL")
# con <- dbConnect(drv, user = "postgres", 
#                  host = "138.197.168.220",
#                  password = "PowerOfBEC", port = 5432, 
#                  dbname = "cciss")
# 
# ##code to check that none have the same predictions
# allSites <- dbGetQuery(con,"select distinct rast_id from pts2km_future")
# #selectSites <- sample(allSites$rast_id, size = 50000, replace = F)
# selectSites <- allSites$rast_id %>% as.integer
# dat <- dbGetQuery(con,paste0("select * from pts2km_future where rast_id IN (",
#                              paste(selectSites,collapse = ","),") and futureperiod = '2041-2060' and scenario = 'ssp245'"))
# setDT(dat)
# dat <- dcast(dat,rast_id ~ gcm,value.var = "bgc_pred", fun.aggregate = function(x)x[1])
# mods <- names(dat)[-1]
# dat[,rast_id := NULL]
# 
# for(i in 1:(length(mods)-1)){
#   for(j in (i+1):length(mods)){
#     if(all(dat[,..i] == dat[,..j])){
#       cat("Predictions", mods[i],"and",mods[j], "are identical!")
#     }
#     cat("Models:",mods[i],mods[j],"\n")
#     temp <- dat[,..i] == dat[,..j]
#     print(table(temp))
#   }
# }
# fwrite(dat, "./outputs/BGC_predictions_2km_2050s_rcp45.csv")
```

# 1. Comparison of predicted ratio of BGC subzone/variants from all GCM models
```{r create data matrix, include=FALSE}
dat <- fread("./outputs/BGC_predictions_2km_2050s_rcp45.csv")
dat2 <- dat %>% rowid_to_column("ID")
dat.long <- dat2 %>% pivot_longer(!ID, names_to = 'gcm', values_to = 'bgc') %>% dplyr::select(-ID) 
dat.sum <- dat.long %>% group_by(gcm, bgc) %>% summarize(count = n()) %>% data.table
dat.matrx <- matrify(dat.sum)# %>% scale()

dat.long2 <- dat.long %>% filter(!gcm %in% c("CanESM5", "UKESM1-0-LL", "INM-CM5-0"))
dat.sum2 <- dat.long2 %>% group_by(gcm, bgc) %>% summarize(count = n()) %>% data.table
dat.matrx2 <- matrify(dat.sum2)
```


### 1a. Optimal cluster groups 

``` {r cluster analysis all, echo = F, result = F, messages = FALSE, warning = 'hide'}
n_clust <- fviz_nbclust(dat.matrx, kmeans, k.max = 8,method = "silhouette")#+
plot(n_clust) ## "optimal" cluster number
n_clust<-n_clust$data
best.clust<-as.numeric(n_clust$clusters[which.max(n_clust$y)])
```

### 1b. Cluster Analysis of 2050s rcp45 BGC predictions by GCM (all GCMs)

```{r output dendrogram, warning=FALSE}
#best.clust <- 3
gcm_clst <- hcut(dat.matrx, k = best.clust, hc_method = "ward.D2", hc_metric = "euclidean")
gcm_dend <- fviz_dend (gcm_clst ,  color_labels_by_k = T, lwd = .5,
                       rect = T, cex = .5, horiz = T, scale = "none") %>% 
  plot()
ggsave("./outputs/GCM_ClusterDendrogram_2km_euclid.jpeg")
```

### 1c. Principle Components with GCM clusters (all GCMs)

```{r output PCO}
# Visualize
fviz_cluster(gcm_clst, data = dat.matrx,
             ellipse.type = "convex",
             palette = "jco",
             ggtheme = theme_minimal(),
             main = "PCO of GCM clusters")

## clusterability###numbers below 0.5 have low clusterability
res <- get_clust_tendency(dat.matrx, n = nrow(dat.matrx)-1, graph = F)
res$hopkins_stat
```

# 2. Comparison of predicted ratio of BGC subzone/variants with poor GCM models removed

Mahony recommended GCMs removed: CanESM5, UKESM1-0-LL, INM-CM5-0

### 2a. Optimal cluster groups
``` {r cluster analysis reduced, echo = F, result = F, messages = FALSE, warning = F}
n_clust <- fviz_nbclust(dat.matrx2, kmeans, k.max = 8,method = "silhouette")#+
plot(n_clust) ## "optimal" cluster number
n_clust<-n_clust$data
best.clust<-as.numeric(n_clust$clusters[which.max(n_clust$y)])
```

### 2b.Cluster Analysis of 2050s rcp45 BGC predictions by GCM (poor GCMs removed)

```{r output dendrogram 2, warning=FALSE}
#best.clust <- 3
gcm_clst <- hcut(dat.matrx2, k = best.clust, hc_method = "ward.D2", hc_metric = "euclidean")
gcm_dend <- fviz_dend (gcm_clst ,  color_labels_by_k = T, lwd = .5,
                       rect = T, cex = .5, horiz = T) %>% 
  plot()
ggsave("./outputs/GCM_ClusterDendrogram_2km_euclid_removed.jpeg")
```

### 2c. Cluster in Principle Components

```{r output PCO 2}
# Visualize
fviz_cluster(gcm_clst, data = dat.matrx,
             ellipse.type = "convex",
             palette = "jco",
             ggtheme = theme_minimal(),
             main = "PCO of GCM clusters")

## clusterability###numbers below 0.5 have low clusterability
res <- get_clust_tendency(dat.matrx2, n = nrow(dat.matrx2)-1, graph = F)
res$hopkins_stat
```


