---
title: "CCISS"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    logo: www/logo.svg
    favicon: www/favicon.ico
    css: www/style.css
#     theme:
#       version: 4
#       bootswatch: yeti
#       primary: "#003366"
# runtime: shiny_prerendered
    theme : yeti
runtime: shiny_prerendered
---

```{r global, include=FALSE}
suppressPackageStartupMessages({
  library(bccciss)
  library(shiny)
  library(leaflet)
  library(DT)
  library(RPostgres)
  library(plotly)
  library(pool)
})
pool <- dbPool(
  drv = RPostgres::Postgres(),
  dbname = Sys.getenv("BCGOV_DB"),
  host = Sys.getenv("BCGOV_HOST"),
  port = 5432, 
  user = Sys.getenv("BCGOV_USR"),
  password = Sys.getenv("BCGOV_PWD")
)
onStop(function() {
  poolClose(pool)
})
bcgov_tileserver <- Sys.getenv("BCGOV_TILESERVER")
bcgov_tilelayer <- Sys.getenv("BCGOV_TILELAYER")
if (is.null(bcgov_tileserver) || is.null(bcgov_tilelayer)) stop("tileserver env not set")
```

BEC MAP
=====================================

Inputs {.sidebar data-width=550}
-------------------------------------

###### Points of interest

```{r}
# Actions on points
actionButton("upload_button", "Upload", icon("upload"), width=120)
actionButton("add_dialog", "Add", icon("plus"), width=120)
actionButton("delete_button", "Delete", icon("trash-alt"), width=120)
actionButton("clear_button", "Clear", icon("broom"), width=120)

# Points
DT::DTOutput("points_table", width="100%")

# Control results
splitLayout(
  checkboxGroupInput(
    "rcp_scenario",
    "RCP Scenario:",
    selected = "rcp45",
    c("4.5 W/m2" = "rcp45", "8.5 W/m2" = "rcp85")
  ),
  radioButtons(
    "aggregation",
    "Multiple Point Aggregation:",
    c("Individual" = "FALSE", "Averaged by BGC Zone" = "TRUE")
  )
)

# Generate results
actionButton("generate_results", label = "Generate results", icon = icon("plus-square"),
             style = "width:100%; background-color:#003366; color: #FFF")

```

###### Instructions
Click on the map or use table to add points.  
To edit cells, double click a row.  
Hit Ctrl+Enter to submit new values.

Biogeoclimatic Zones + Subzones Variants Map
-------------------------------------
```{r}
leafletOutput("bec_map", height = "auto")

```

FEASIBILITY
=====================================  

Inputs {.sidebar data-width=230}
-------------------------------------

###### Filters  

```{r}
selectInput("siteref_feas", label = "Sites:", choices = character())
selectInput("site_series_feas", label = "Site Series", choices = character())
selectInput("filter_feas", label = "Detailed Feasibility", choices = c("All" = "a", "Feasible Only" = "f"))
```

###### Legend
```{r}
HTML(
  paste0(
    '<svg viewBox="0 0 1 1" height="14px" width="14px"><rect height=1 width=1 style="fill : ',
    c("limegreen", "deepskyblue", "gold", "grey"),
    '" /><span>&nbsp;',
    c("Primary", "Secondary", "Tertiary", "Not Suitable"),
    '</span>',
    collapse = "<br />"
  )
)
```

Species Feasibility {.tabset}
-------------------------------------

### Summary

```{r}
DT::DTOutput("summary_feas", width = "100%", height = "auto")
```

### Detailed

```{r}
DT::DTOutput("detailed_feas", width = "100%", height = "auto")
```
   
SILVICULTURE
=====================================     

Inputs {.sidebar data-width=230}
-------------------------------------

###### Filters  

```{r}
selectInput("siteref_silv", label = "Sites:", choices = character())
selectInput("site_series_silv", label = "Site Series", choices = character())
selectInput("filter_silv", label = "Species Feasibility", choices = c("Feasible Only" = "f", "All" = "a"))
```

Silviculture {.tabset}
-------------------------------------

### Silviculture

```{r}
uiOutput("silviculture_block")
klinka <- tags$small("From Klinka et al. 2000. Ecological and Silvical Characteristics of Tree Species")
```

### Tolerance

```{r}
tags$h5("Tolerance comparisons")
DT::DTOutput("silvics_tol_dt", width = "100%", height = "auto")
klinka
```

### Resistance

```{r}
tags$h5("Resistance and potential risk comparisons")
DT::DTOutput("silvics_resist_dt", width = "100%", height = "auto")
klinka
```

### Regeneration stage

```{r}
tags$h5("Comparison of silvical characteristics; regeneration stage")
DT::DTOutput("silvics_regen_dt", width = "100%", height = "auto")
klinka
```

### Maturing stage

```{r}
tags$h5("Comparison of silvical characteristics; maturing stage")
DT::DTOutput("silvics_mature_dt", width = "100%", height = "auto")
klinka
```

BGC FUTURES
=====================================

Inputs {.sidebar data-width=230}
-------------------------------------

###### Filter

```{r}
selectInput("siteref_bgc_fut", label = "Sites:", choices = character())

```

BGC Futures: ratio of models predicting BGC
-------------------------------------

### Ratio of Models Predicting BGC `r textOutput("current_bgc_fut", inline = TRUE)`

```{r}
plotly::plotlyOutput("bgc_fut_plot", width = "100%", height = "auto")
```

EXPORT
=====================================

Inputs {.sidebar data-width=420}
-------------------------------------

###### Filter

```{r}
actionButton("report_filter_all", label = "Check All", icon = icon("check"))
actionButton("report_filter_none", label = "Uncheck All", icon = icon("ban"))
div(
  checkboxGroupInput("report_filter", label = "Site Series", choices = character(), width = 400),
  style = "line-height: 1.5; color: #222; background-color: #fff; margin: 10px 0px 10px 0px; padding: 0px 10px 0px 10px"
)
```

Export a report on selected points.
-------------------------------------

### Export a report on selected points

```{r}
dl_style <- "max-width: 300px; width:100%; height: 40px !important;"
textInput("report_name", "Name", value = "report")
selectInput("report_format", "Format", c("html", "pdf"))
span(downloadButton("report_download", "Download", style = dl_style), id = "download_span")
```

How the CCISS tool works {data-navmenu="ABOUT"} 
=====================================

The Climate Change Informed Species Selection Decision Aid provides information on future tree species suitability in British Columbia. It combines future climate information with species viability models to illustrate how likely each species is to thrive in the range of potential futures.  

The CCISS tool reassesses the suitability ranks of species at a site series level under multiple plausible modelled future climates. Understanding climate- and site-level species suitability is one of the foundational pieces of information that a forester requires for the creation of successful silvicultural prescriptions over a rotation. The CCISS tool looks at near- and mid-term projected changes to BGC climates and the implications to species suitability. The tool then aligns the projected future suitability rank of species at a POI with the suitability in the default stocking standards outlined in the Chief Forester’s Reference Guide to highlight where there are predicted climate change induced shifts in species suitability. This information can be used to inform planting/ silvicultural prescription outlined in climate change informed stocking standard. The CCISS tool is spatial explicit to account for the gradient of climate change that will different regions and elevations of a BGC.  
  
[Would you like to know more?](https://www.for.gov.bc.ca/ftp/HRE/external/!publish/CCISS/CCISS_in_Stocking%20Standards.pdf)

Shiny app information {data-navmenu="ABOUT"} 
=====================================

Shiny host: `r system("hostname", intern = TRUE)`  
Database host: `r Sys.getenv("BCGOV_HOST")`  
Tiles source: `r Sys.getenv("BCGOV_TILESERVER")`  
Github: [bcgov/CCISS_ShinyApp](https://github.com/bcgov/CCISS_ShinyApp)  
  
Copyright 2021 Province of British Columbia  
  
[LICENSE](http://www.apache.org/licenses/LICENSE-2.0)

```{r}
tags$script(HTML('
  Shiny.addCustomMessageHandler("jsCode",
    function(message) {
      console.log(message)
      eval(message.code);
    }
  );'
))

```

```{r server, context = "server"}
# bslib::bs_themer()
source("./server/common.R", local = TRUE)
source("./server/generate.R", local = TRUE)
source("./server/points.R", local = TRUE)
source("./server/map.R", local = TRUE)
source("./server/feasibility.R", local = TRUE)
source("./server/silviculture.R", local = TRUE)
source("./server/futures.R", local = TRUE)
source("./server/download.R", local = TRUE)
```
