---
title: "CCISS BEC"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    logo: www/logo.svg
    favicon: www/favicon.ico
    theme: flatly
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
suppressPackageStartupMessages({
  library(bccciss)
  library(shiny)
  library(leaflet)
  library(DT)
  library(bcmaps)
})

# Again this could be done with postgis instead
bec <- bcmaps::bec(ask = FALSE)
# Trick to make intersect faster by prefiltering with bbox
classes <- attr(bec, "class")
# reclass as data.table to allow data.table operation
setDT(bec)
data.table::set(
  bec,
  j = c("xmin", "ymin", "xmax", "ymax"),
  value = data.table::rbindlist(lapply(bec$geometry, function(x) as.list(sf::st_bbox(x))))
)
# and back into an sf
attr(bec, "class") <- classes

```


BEC MAP
=====================================  

Inputs {.sidebar data-width=500}
-------------------------------------

#### Points
<hr>  
Click on the map to add points or enter data below. Double click row to edit. Ctrl+Enter to confim,

```{r}
actionButton("add_button", "Add", icon("plus"))
actionButton("delete_button", "Delete", icon("trash-alt"))
actionButton("upload_button", "Upload", icon("upload"))
actionButton("clear_button", "Clear", icon("broom"))
DT::DTOutput("points_table", width="100%")
selectInput("rcp_scenario", "RCP Scenario:", selected = "4.5", c("4.5", "8.5"), multiple = TRUE, width = 150)
radioButtons("aggregation", "Multiple Point Aggregation:", c("Individual" = FALSE, "Averaged by BGC Zone" = TRUE), inline = TRUE)
```

[How the CCISS tool works](./#section-how-the-cciss-tool-works)

Biogeoclimatic Zones + Subzones Variants Map
-------------------------------------
```{r}
leafletOutput("bec_map", width = "100%", height = "100%")

```

SPECIES SUITABILITY
=====================================     

### Species Suitability

Site Series
{insert name of site series}

Predicted Suitability

```{r}
```
   
SILVICULTURE
=====================================     

### Silviculture

Site Series
{insert name of site series}

Forest Region:
    
```{r}
```


BGC FUTURES
=====================================     

### BGC Futures: ratio of models predicting BGC

Current BGC : {insert current}
 
```{r}
```

... to PDF {data-navmenu="EXPORT" .navbar-right}
=====================================

... to HTML {data-navmenu="EXPORT" .navbar-right}
=====================================

How the CCISS tool works {data-navmenu="ABOUT"} 
=====================================

The Climate Change Informed Species Selection Decision Aid provides information on future tree species suitability in British Columbia. It combines future climate information with species viability models to illustrate how likely each species is to thrive in the range of potential futures.  

The CCISS tool reassesses the suitability ranks of species at a site series level under multiple plausible modelled future climates. Understanding climate- and site-level species suitability is one of the foundational pieces of information that a forester requires for the creation of successful silvicultural prescriptions over a rotation. The CCISS tool looks at near- and mid-term projected changes to BGC climates and the implications to species suitability. The tool then aligns the projected future suitability rank of species at a POI with the suitability in the default stocking standards outlined in the Chief Forester’s Reference Guide to highlight where there are predicted climate change induced shifts in species suitability. This information can be used to inform planting/ silvicultural prescription outlined in climate change informed stocking standard. The CCISS tool is spatial explicit to account for the gradient of climate change that will different regions and elevations of a BGC.  
  
[Would you like to know more?](https://www.for.gov.bc.ca/ftp/HRE/external/!publish/CCISS/CCISS_in_Stocking%20Standards.pdf)


```{r server_elements, context="server"}

# Proxy objects
DT_proxy <- DT::dataTableProxy("points_table")
map_proxy <- leaflet::leafletProxy('bec_map')

# Input management ----

## Points dataframe
uData <- session$userData
uData$bec <- bec

uData$points <- uData$basepoints <- data.table(
  ID = integer(),
  Latitude = numeric(),
  Longitude = numeric(),
  Elevation = numeric(),
  BGC = character()
)

output$points_table <- DT::renderDataTable({
  DT::datatable(
    uData$points, rownames = FALSE,
    options = list(searching = FALSE, lengthChange = TRUE, pageLength = 5),
    editable = list(target = "row", disable = list(columns = c(0,4)))
  )
})

## Points update logic
update_points <- function(data) {
  if (!missing(data)) {
    data[, Latitude := round(Latitude, 5)]
    data[, Longitude := round(Longitude, 5)]
    uData$points <- rbindlist(list(uData$points, data), fill = TRUE)
    uData$points[, ID := seq_len(nrow(uData$points))]
  }
  non_na_idx <- which(!is.na(uData$points$Longitude) & !is.na(uData$points$Latitude))
  # Using a local sf object, this should be a postgis database call
  # This data is not feeded to points DT in UI but feeds popups
  if (length(non_na_idx) > 0L) {
    bec_info <- localGetBecInfo(uData$points[i = non_na_idx], "Longitude", "Latitude", uData$bec)
    uData$points[i = non_na_idx, BGC := bec_info$BGC_LABEL]
    # TODO
    # Fetch elevation from where?
    popups <- bec_info[, paste("<b>", names(.SD), ":</b>", .SD, collapse = "<br />"), by=1:NROW(bec_info)]$V1
    uData$points[i = non_na_idx, popups := sapply(popups, htmltools::HTML)]
    map_proxy %>%
    leaflet::clearMarkers() %>%
    leaflet::addCircleMarkers(lng = ~Longitude, lat = ~Latitude,
                              data = uData$points[i = non_na_idx],
                              radius = 4, color = "#333", fillColor = "red", stroke = TRUE,
                              fillOpacity = 0.4, opacity = 0.8, weight = 2,
                              popup = ~popups)
    uData$points[, popups := NULL]
  }
  DT::replaceData(DT_proxy, uData$points, clearSelection = "all", rownames = FALSE)
}

## Upload points logic
observeEvent(input$upload_button, priority = 20,{
  upload_form("upload_button")
})

upload_form <- function(button_id){
  showModal(
    modalDialog(
      fileInput(inputId = "points_upload", label =  "Upload points in a delimited files",
                accept = c(".csv", ".txt"), buttonLabel = "Browse...", placeholder = "My points")
    )
  )
}

observeEvent(input$points_upload, priority = 20,{
  append_points_file(input$points_upload$datapath)
  removeModal()
})

append_points_file <- function(datapath){
  points <- fread(datapath)
  lat_match <- head(grep("^lat|latitude", names(points), ignore.case = TRUE), 1)
  lng_match <- head(grep("^lng|^long|longitude", names(points), ignore.case = TRUE), 1)
  ele_match <- head(grep("^elev|elevation", names(points), ignore.case = TRUE), 1)
  update_points(
    data.table(
      Latitude = {if (length(lat_match) > 0L) {as.numeric(points[[lat_match]])} else NA_real_},
      Longitude = {if (length(lng_match) > 0L) {as.numeric(points[[lng_match]])} else NA_real_},
      Elevation = {if (length(ele_match) > 0L) {as.numeric(points[[ele_match]])} else NA_real_}
    )
  )
}

## Add a point logic
observeEvent(input$add_button, priority = 20,{
  update_points(data.table(ID = NA))
})

## Delete selected points logic
observeEvent(input$delete_button, priority = 20,{
  
  if(length(input$points_table_rows_selected)>=1) {
    uData$points <- uData$points[-input$points_table_rows_selected]
    update_points()
  } else {
    showModal(
      modalDialog(
        title = "Warning",
        paste("Please select row(s)." ),
        easyClose = TRUE
      )
    )
  }
})

## Clear all points logic
observeEvent(input$clear_button, priority = 20,{
  uData$points <- uData$basepoints
  update_points()
})

## Edit points logic
observeEvent(input$points_table_cell_edit, {
  info = input$points_table_cell_edit
  # col is 0-indexed because not using rownames
  set(uData$points, info$row[1], info$col + 1L, as.list(as.numeric(info$value)))
  update_points()
})

# Map ----

output$bec_map <- renderLeaflet({
  bccciss_map()
})

## Map click logic
observeEvent(input$bec_map_click, {
  pos <- input$bec_map_click
  update_points(data.table(Latitude = pos$lat, Longitude = pos$lng))
})


```
