---
title: "Species name (abbrv)"
format: 
  dashboard:
    scrolling: true
    orientation: rows
---

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(gt)
```




# Current range

## Summary text

Summary text box. Should take up the full row

## Current range maps

### Current B2

```{r}
#| title: Current B2 map
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Placeholder plot") +
  theme_classic()

```

Figure caption for panel 1

### Current C4

```{r}
#| title: Current C4 map
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Placeholder plot") +
  theme_classic()
```
Figure caption for panel 2

### Current D6

```{r}
#| title: Current D6 map
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Placeholder plot") +
  theme_classic()
```
Figure caption for panel 3







# CCISS projections

## Overall summary

Overall summary text describing future trends for this species. maybe some preface text to get user oriented to what to look for below.



## Overall trends

### Column - Bubble plot

```{r}
#| title: Bubble plot showing ensemble mean for each edatope
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Placeholder plot") +
  theme_classic()
```

### Column - Plot description

Text to describe the bubble plot

## Shifts in BGC suitability

Text to describe shifts in BGC suitability

## Plots

### A - Changes in suitability: map {.tabset} 

#### B2

```{r}
#| title: Map showing overall mean change in suitability (2081-2100)

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Placeholder plot") +
  theme_classic()
```
 
#### C4

```{r}
#| title: Map showing overall mean change in suitability (2081-2100)

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Placeholder plot") +
  theme_classic()
```

#### D6

```{r}
#| title: Map showing overall mean change in suitability (2081-2100)

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Placeholder plot") +
  theme_classic()
```
 
### B - Mean change box plot
```{r}
#| title: Boxplot showing mean change in suitability in each BGC zone

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Placeholder plot") +
  theme_classic()
```

## Figure captions for A and B above

Text summarizing the trends in the plots above, as a combined figure caption

## Suitability area

### Total suitable area change

```{r}
#| title: Plot showing the change in total suitable area between historical and far future (stacked bar plot and/or donut plot) AND spaghetti plots (3-panel plot (by edatope) showing the ensemble variation)
#| layout-ncol: 2

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Total suitable area by BGC zone") +
  theme_classic()

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Spaghetti plots") +
  theme_classic() +
  facet_wrap(~Species, ncol = 3)

```


## Figure descriptions

 Text to describe the two plots above
 
## Areas of interest

Regions of interest:
Text and maps and/or plots zooming in to any particular geographic areas of interest

## Elevational patterns

Elevational patterns: Text to summarize

### Elevation plots


```{r}
#| title: Plot showing the change in total suitable area between historical and far future (stacked bar plot and/or donut plot) AND spaghetti plots (3-panel plot (by edatope) showing the ensemble variation)
#| layout-ncol: 3

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Elevation plot 1") +
  theme_classic()

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Elevation plot 2") +
  theme_classic()

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  labs(title = "Elevation plot 3") +
  theme_classic()

```





# Forest health

## Text row

Page describing the potential forest health considerations for each species, as appropriate



# Additional resources

| Resource | Description |
|-----------------------|-------------------------------------------------|
| [Tree Species Compendium](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/silviculture/tree-species-selection/tree-species-compendium-index) | Descriptions and characteristics of tree species found in British Columbia and comparison information regarding each species ecological suitability and tolerances to a variety of external factors. |
| Another link | description |
|  |  |
|  |  |
|  |  |
|  |  |
|  |  |
|  |  |
|  |  |
|  |  |
